\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-14 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
modifs supplementaires

Our paper also relates to \cite{Kropf-Saure-JIE-2016}, who estimate the size and shape of per-shipment costs based on Swiss data, and to \cite{Alessandria-et-al-AER-2010} or \cite{Hornok-et-al-RES-2015, Hornok-et-al-JIE-2015}. While \cite{Alessandria-et-al-AER-2010}  and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating some ``lumpiness'' in international trade transactions, \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment (i.e., additive by nature), and draw welfare conclusions regarding the variations of these costs. Also closely related to our paper is the work by \cite{Irrazabal_2015}, which develops a structural framework for inferring relative additive trade costs from firm-level trade data. Implementing their methodology on Norwegian firm-level export data for the year 2004, they find that, for the median shipment, additive costs (in Norwegian crowns) amount to 6\% of the export price multiplied by the ad-valorem cost (also expressed in Norwegian crowns). Our results share in common with \cite{Irrazabal_2015} the important role of the additive component of international trade costs, and a welfare analysis of the latter. Compared to

@@

In this section, we explore the implications of our empirical results on theoretical grounds. While the bulk of the trade literature investigates the role of trade costs modelled as ad-valorem costs (e.g., iceberg trade costs), not much is said about the role of the additive component. One potential explanation is the lack of empirical estimates about the size of additive costs. Our results may thus usefully palliate this limitation. Specifically, we make use of our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two cases: when this reduction is achieved through a combined reduction in the ad-valorem and the additive
components (as quantified by our empirical model) or solely through the ad-valorem cost (as standardly modelled in New Trade theoretical approaches). To this aim, we embed additive costs in the canonical \citet{melitz} model.\smallskip

@@

That said, it should be noted the case with additive costs in \cites{Lashkaripour_JIE2020} paper relies on a negligible share of additive costs. In this context, one might expect that whether additive costs are present or not makes little difference. As underlined by \cite{Lashkaripour_JIE2020}, a second explanation may rely on the modeling framework. While \cite{Lashkaripour_JIE2020} relies on a perfectly competitive environment, we use a model with monopolistic competition and firm selection \`{a} la \cite{melitz} or \cite{chaney2008}, as did \cite{sorensen2014} and \cite{Irrazabal_2015}. In this setting, we show that additive costs do modify the selection of firms on both the domestic and the export markets, e.g the extensive margin of trade, whose role in the welfare gains of trade liberalization lies at the heart of the New Trade models  \`{a} la \cite{melitz}. Put differently, leaving aside the selection issue leads to underestimate the welfare gains that can be achieved by a reduction in the additive component of transport costs.

>>>>

Our paper also relates to \cite{Kropf-Saure-JIE-2016}, who estimate the size and shape of per-shipment costs based on Swiss data, and to \cite{Alessandria-et-al-AER-2010} or \cite{Hornok-et-al-RES-2015, Hornok-et-al-JIE-2015}. While \cite{Alessandria-et-al-AER-2010}  and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating some ``lumpiness'' in international trade transactions, \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment (i.e., additive by nature), and draw welfare conclusions regarding the variations of these costs. Also closely related to our paper is the work by \cite{Irrazabal_2015}, which develops a structural framework for inferring relative additive trade costs from firm-level trade data. Implementing their methodology on Norwegian firm-level export data for the year 2004, they find that, for the median shipment, additive costs (in Norwegian crowns) amount to 6\% of the export price multiplied by the ad-valorem cost (also expressed in Norwegian crowns). Our results share in common with \cite{Irrazabal_2015} the important role of the additive component of international trade costs, and a welfare analysis of the latter.

@@

In this section, we explore the implications of our empirical results on theoretical grounds. Over the last decade, several papers examined the implications of additive/per-shipment costs. \cite{Kropf-Saure-JIE-2016} estimate the size and shape of per-shipment costs based on Swiss data. \cite{Alessandria-et-al-AER-2010} and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating ``lumpiness'' in international trade transactions. \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment (i.e., additive by nature), and draw welfare conclusions regarding the variations of these costs. We complement these various outcome by providing a long-run characterization of both additive and multiplicative component of transports costs. Second, we make use of our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two cases: when this reduction is achieved through a combined reduction in the ad-valorem and the additive components (as quantified by our empirical model) or solely through the ad-valorem cost (as standardly modelled in New Trade theoretical approaches). To this aim, we embed additive costs in the canonical \citet{melitz} model.\smallskip
%While the bulk of the trade literature investigates the role of trade costs modelled as ad-valorem costs (e.g., iceberg trade costs), not much is said about the role of the additive component. One potential explanation is the lack of empirical estimates about the size of additive costs. Our results may thus usefully palliate this limitation.

@@

That said, it should be noted the case with additive costs in \cites{Lashkaripour_JIE2020}paper relies on a negligible share of additive costs. In this context, one might expect that whether additive costs are present or not makes little difference. As underlined by \cite{Lashkaripour_JIE2020}, a second explanation may rely on the modeling framework. While \cite{Lashkaripour_JIE2020} relies on a perfectly competitive environment, we use a model with monopolistic competition and firm selection \`{a} la \cite{melitz} or \cite{chaney2008}, as did \cite{sorensen2014} and \cite{Irrazabal_2015}. In this setting, we show that additive costs do modify the selection of firms on both the domestic and the export markets, e.g the extensive margin of trade, whose role in the welfare gains of trade liberalization lies at the heart of the New Trade models  \`{a} la \cite{melitz}. Put differently, leaving aside the selection issue leads to underestimate the welfare gains that can be achieved by a reduction in the additive component of transport costs.
